Challenging Fuel Cycle Modeling Assumptions: Facility and Time Step Discretization Effects

### 2015-10-21 paper.tex
commas in vals in tables

\begin{table}[h]
    \caption{Reactor Facility Parameters}
    \centering
    \begin{tabular}{ |r | c c | }
        \hline                       
            & LWR & SFR \\
        \hline                       
        Lifetime (yr)         & 80 & 80 \\
        Cycle length (months) & 18 & 15 \\
        Batch size (kg)       & 29565 & 8025 \\
        Batches per core      & 3 & 5 \\
        \hline                       
    \end{tabular}
    \captionsetup{justification=centering}
    \label{tab:reactors}
\end{table}

@@

\begin{table}
    \captionsetup{justification=centering}
    \caption{Reactor Parameter Invariants}
    \centering
    \begin{tabular}{ |r | c c | }
        \hline                       
                                                                             & LWR      & SFR      \\
        \hline                       
                                                                             &          &          \\
        Discharge Rate ($\frac{\text{kg} \cdot \text{HM}}{\text{month}}$)           & 1642.5   & 535      \\
                                                                             &          &          \\
        Burnup  ($\frac{\text{MWe} \cdot \text{month}}{\text{kg} \cdot \text{HM}}$) & 0.547945 & 0.672897 \\
                                                                             &          &          \\
        Effective Power  ($\text{MWe}$)                                      & 900      & 360      \\
                                                                             &          &          \\
        Core Size  ($\text{kg} \cdot \text{HM}$)                                    & 88695    & 40125    \\
                                                                             &          &          \\
        \hline                       
    \end{tabular}
    \label{tab:invar}
\end{table}

>>>>

\begin{table}[h]
    \caption{Reactor Facility Parameters}
    \centering
    \begin{tabular}{ |r | c c | }
        \hline                       
            & LWR & SFR \\
        \hline                       
        Lifetime (yr)         & 80 & 80 \\
        Cycle length (months) & 18 & 15 \\
        Batch size (kg)       & 29,565 & 8,025 \\
        Batches per core      & 3 & 5 \\
        \hline                       
    \end{tabular}
    \captionsetup{justification=centering}
    \label{tab:reactors}
\end{table}

@@

\begin{table}
    \captionsetup{justification=centering}
    \caption{Reactor Parameter Invariants}
    \centering
    \begin{tabular}{ |r | c c | }
        \hline                       
                                                                             & LWR      & SFR      \\
        \hline                       
                                                                             &          &          \\
        Discharge Rate ($\frac{\text{kg} \cdot \text{HM}}{\text{month}}$)           & 1,642.5   & 535      \\
                                                                             &          &          \\
        Burnup  ($\frac{\text{MWe} \cdot \text{month}}{\text{kg} \cdot \text{HM}}$) & 0.547945 & 0.672897 \\
                                                                             &          &          \\
        Effective Power  ($\text{MWe}$)                                      & 900      & 360      \\
                                                                             &          &          \\
        Core Size  ($\text{kg} \cdot \text{HM}$)                                    & 88,695    & 40,125    \\
                                                                             &          &          \\
        \hline                       
    \end{tabular}
    \label{tab:invar}
\end{table}
